Import libraries and create surveys_complete.

```{r}
library(tidyverse)
download.file(url="https://ndownloader.figshare.com/files/2292169", 
              destfile = "portal_data_joined.csv")
surveys <- read_csv("portal_data_joined.csv")
surveys_complete <- surveys %>%  
  filter(!is.na(weight),    
         !is.na(hindfoot_length), 
         !is.na(sex))
```

Use ggplot() to plot the data. (Should get blank canvas.)

```{r}
ggplot(data = surveys_complete)
```

Aesthetic mapping - assign weight to x-axis, hindfoot_length to y-axis.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length))
```

Make points show up by adding geom_point()

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length)) +
  geom_point()
```

Change transparency of points.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length)) +
    geom_point(alpha = 0.1)
```

Change color of points.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length)) +
    geom_point(alpha = 0.1, color = "blue")
```

Color points according to species_id.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length)) +
    geom_point(alpha = 0.1, aes(color = species_id))
```

Move color into the ggplot() function as an additional aesthetic mapping.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length, color = species_id)) +
    geom_point(alpha = 0.1)
```

Map jitter instead of points.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = weight, y = hindfoot_length, color = species_id)) +
    geom_jitter(alpha = 0.1)
```

Map the data as a boxplot.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = species_id, y = weight)) +
    geom_boxplot()
```

Map the data as a boxplot and add jitter.

```{r}
ggplot(data = surveys_complete, mapping = aes(x = species_id, y = weight)) +
    geom_boxplot(alpha = 0) +
    geom_jitter(alpha = 0.3, color = "tomato")
```


